HERMES : Hybrid ERror-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2021-12-10 hermes_paper/hermes_paper.tex
Minor changes

In theoretical fashion dynamics \citep{rogersdiffusion}, different categories of adopters follow a trend in succession, resulting in several adoption waves. In this way, we add to our large dataset several weak signals for each sequence.
Firstly, we created a specific fashion-oriented panel of micro-influencers. With the same methodology than our main signals, we can represent our fashion trends life on social media on this specific population. we named \textit{fashion-forwards} this first weak signal. For instance, an impressive emerging fashion shoes trend with its linked \textit{fashion-forwards} weak singal is represented in Figure~\ref{fig:oneemergingtrend}. 
let $\ts_t^{f,n}$ be the value of the $n$-th \textit{fashion-forwards} sequence at time $t$ and  $\fullts^{f,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.
As we want to detect shifts between our main signal and our fashion forward signal and also normalize our weak signal, we compute the following input for our hybrid model :
for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
$$
\ws^{f,n}_{t} = \frac{\ts_t^{f,n}}{\ts_t^{f,n}+\ts_t^{n}}
$$

Secondly, we analyzed only specific parts of social media users depending on the number of followers. With three thresholds, 0-1350,1350-7000 and 7000+, we created the following external signals : \textit{followers-low}, \textit{followers-mid} and \textit{followers-high}. Again, the motivation here is to detect behaviour gaps between these three segments that could announce bigger changes in the main signal. let $\ts_t^{l,n}$,$\ts_t^{m,n}$ and $\ts_t^{h,n}$ be the value of the $n$-th \textit{followers-low},\textit{followers-mid} and \textit{followers-high} sequence at time $t$ and  $\fullts^{l,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{m,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{h,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of these sequences. Based on them, we compute 2 inputs for our hybrid model : for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,

@@

At the end, we created 3 weak signals $\ws^{l}$,$\ws^{l}$ and $\ws^{h}$. They are frequently sparse for micro trends and they often lack interest in common fashion trends. However, in several examples, they are fundamental to detect the future fashion evolution.

@@

To train our hybrid model, we split our dataset into three blocks, train, eval and test sets. We use the 3 first years as our train set, we keep the 4th year for our eval set and we hide the last year for our test set. We train our hyrid model to compute a one-year ahead prediction, $\lag$ equal to 52, and we set the window size $\window$ equal to 104.
Using the two first year of our train set, we fit a first per-time-series parametric model for each time series. With the resulting collection of local models, we compute a first forecast of the third year for each sequence. Using these forecasts, we preprocess our time series and finally determine our RNN inputs. In the same way, for the eval set, we fit a second time our per-time-series predictors using the three first years and we forecast the fourth year. We preprocess our time series and we evaluate how our error-corrector RNN is able to improve the first collection of predictions of the fourth year.
At the end, we repeat the same process for the fifth year and compute our final accuracy measures. An example of our temporal split is shown in  Figure~\ref{fig:train_eval_test_set}.
%We train our hyrid model to compute a one-year ahead prediction with $\window$ equal to 104 and a $\lag$ equal to 52. For each time series, we fitted 3 per-time-series parametric models: We fit the first one using the 2 first years and compute a forecast of the thrid year.

>>>>

In theoretical fashion dynamics \citep{rogersdiffusion}, different categories of adopters follow a trend in succession, resulting in several adoption waves. In this way, we add to our large dataset several weak signals for each sequence.
Firstly, we created a specific fashion-oriented panel of micro-influencers. With the same methodology than for target signals, we can represent  fashion trends life on social media on this specific population. we named \textit{fashion-forwards} this first weak signal. For instance, an impressive emerging fashion shoes trend with its linked \textit{fashion-forwards} weak signal is represented in Figure~\ref{fig:oneemergingtrend}. 
let $\ts_t^{f,n}$ be the value of the $n$-th \textit{fashion-forwards} sequence at time $t$ and  $\fullts^{f,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.
As we want to detect shifts between target signals and and fashion forward signal and also normalize the weak signal, we compute the following input for our hybrid model:
for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
$$
\ws^{f,n}_{t} = \frac{\ts_t^{f,n}}{\ts_t^{f,n}+\ts_t^{n}}\,.
$$

Secondly, we analyzed only specific parts of social media users depending on the number of followers. With three thresholds, 0-1350,1350-7000 and 7000+, we created the following external signals : \textit{followers-low}, \textit{followers-mid} and \textit{followers-high} \textcolor{red}{Pas clair}. Again, the motivation here is to detect behaviour gaps between these three segments that could announce bigger changes in the main signal. let $\ts_t^{l,n}$,$\ts_t^{m,n}$ and $\ts_t^{h,n}$ be the value of the $n$-th \textit{followers-low},\textit{followers-mid} and \textit{followers-high} sequence at time $t$ and  $\fullts^{l,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{m,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$, $\fullts^{h,n} = \{\ts_t^{f,n}\}_{1\leqslant t \leqslant T}$ be all the values of these sequences. Based on them, we compute two inputs for our hybrid model : for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,

@@

Therefore, we created three weak signals $\ws^{l}$,$\ws^{l}$ and $\ws^{h}$. They are frequently sparse for micro trends and they often lack interest in common fashion trends. However, in several examples, they are fundamental to detect the future fashion evolution, \textcolor{red}{as illustrated in Section~\ref{}}.

@@

We split the dataset into three blocks, train, eval and test sets. We use the 3 first years as train set, keep the 4th year for the evaluation set and hide the last year for the test set. We trained the hyrid model to compute a one-year ahead prediction, $\lag$ equal to 52, and we set the window size $\window$ equal to 104.
Using the two first year of the train set, we fit a first per-time-series parametric model for each time series. With the resulting collection of local models, we compute a first forecast of the third year for each sequence. Using these forecasts, we preprocess  time series and finally compute the RNN inputs. In the same way, for the eval set, we fit a second time our per-time-series predictors using the three first years and we forecast the fourth year. We preprocess time series and evaluate how the error-corrector RNN is able to improve the first collection of predictions of the fourth year. The same process is repeated for the fifth year and compute our final accuracy measures. An example of our temporal split is shown in  Figure~\ref{fig:train_eval_test_set}.
%We train our hyrid model to compute a one-year ahead prediction with $\window$ equal to 104 and a $\lag$ equal to 52. For each time series, we fitted 3 per-time-series parametric models: We fit the first one using the 2 first years and compute a forecast of the thrid year.
